### 2013-11-19 research/paper/figure/cy_vs_theta.tex
uploaded with Kenny's corrections

  \caption{Lift coefficient, $C_y$ \JL{$C_y$ is upper case here, lower case on the figure. Make them match what is in the nomenclature}, as a function of incidence angle $\theta$, for a static square cross section. (a) Data from simulations at $Re=165$  (b) data from \cite{Parkinson1964} at $Re=22300$. Points ($\bullet$) are measurements from the simulations. The solid lines in both plots are 7th-order interpolating polynomial used to predict the fluid forcing for the QSS model.}
    \label{fig:lift_curves}
\end{figure}

>>>>

  \caption{Lift coefficient, $C_y$, as a function of incidence angle $\theta$, for a static square cross section. (a) Data from simulations at $Re=165$  (b) data from \cite{Parkinson1964} at $Re=22300$. Points ($\bullet$) are measurements from the simulations. The solid lines in both plots are 7th-order interpolating polynomial used to predict the fluid forcing for the QSS model. $C_y$ is the force coefficient of the force which occurs normal to the induced velocity.}
    \label{fig:lift_curves}
\end{figure}

### 2013-11-19 research/paper/figure/uncollapsed_data.tex
new files added
uploaded 12.01 11/11 2013
uploaded with Kenny's corrections

    \put(0.00,0.685){$\frac{A}{D}$}
%    \put(0.52,1.075){$\frac{A}{D}$}
    \put(0.00,0.44){$\frac{V}{D}$}
%    \put(0.52,0.83){$\frac{V}{D}$}
    \put(-0.01,0.15){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
%    \put(0.5,0.54){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

@@

%  \vspace{-4cm}
  \caption{Velocity amplitude, displacement amplitude and mean power  as functions of $U^*$. Data presented in (a), (c) and (e) were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}). Data presented in (b),(d) and (f) were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+). The multiple branches for the higher Re are due to the hysteresis between two solutions.}

>>>>

    \put(0.00,0.6){$\displaystyle\frac{A}{D}$}
%    \put(0.52,1.075){$\frac{A}{D}$}
    \put(0.00,0.4){$\displaystyle\frac{V}{D}$}
%    \put(0.52,0.83){$\frac{V}{D}$}
    \put(-0.025,0.15){$\displaystyle\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
%    \put(0.5,0.54){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

@@

%  \vspace{-4cm}
  \caption{Velocity amplitude, displacement amplitude and mean power  as functions of $U^*$. Data presented in (a), (c) and (e) were calculated using input data at $Re=22300$ and $m^*=1163$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}). Data presented in (b),(d) and (f) were obtained using input data at $Re=165$ and $m^*=20$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+). The multiple branches for the higher Re are due to the hysteresis between two solutions.}

### 2013-11-19 research/paper/nomenclature.tex
uploaded with Kenny's corrections

\begin{tabular}{ll}
$a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
$C_y$ & instantaneous force coefficient normal to the freesream velocity \\
$F_y$ & force due to $C_y$  \\ 
$\rho$ & fluid density  \\
$m$ & mass of the body \\
$m_a$ & added mass \\
$c$ & damping constant/damping factor \\
$k$ & spring constant \\
$U_i$ & induced velocity \\
$\theta$ & induced angle of incidence \\
$U$ & freestream velocity \\
$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration   \\
$A$ & displacement amplitude\\
$\mathcal{A}$ & cross sectional area\\ 
$F_0$& force due to shedding \\
$\omega_s$& vortex shedding frequency \\
$t$ & time \\
$P_{mean}$& mean power \\
$f=\frac{1}{2\pi}\sqrt{\frac{k}{m}}$& natural frequency of the system \\
$\omega_n= 2 \pi f$& natural frequency of the system  \\
$D$ & characteristic length of the body  \\
$m^*=\frac{m}{\rho \times \text{Volume of the body}}$& mass ratio \\
$U^*=\frac{U}{f \times D}$& reduced velocity  \\
$\zeta= \frac{c}{2 m \omega_n}$& damping ratio \\
$P_t$   & power transferred to the body by the fluid \\
$P_d$& power dissipated due to mechanical damping  \\
$Re$& Reynolds number  \\
$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle \\
& \\
& \\
\end{tabular}

>>>>

\begin{tabular}{ll}
$a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
$C_y$ & instantaneous force coefficient normal to the induced velocity \\
$F_y$ & force due to $C_y$  \\ 
$\rho$ & fluid density  \\
$m$ & mass of the body \\
$m_a$ & added mass \\
$c$ & damping constant/damping factor \\
$k$ & spring constant \\
$U_i$ & induced velocity \\
$\theta$ & induced angle of incidence \\
$U$ & freestream velocity \\
$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration   \\
$A$ & displacement amplitude\\
$\mathcal{A}$ & cross sectional area\\ 
$F_0$& force due to shedding \\
$\omega_s$& vortex shedding frequency \\
$t$ & time \\
$P_{mean}$& mean power \\
$f=\frac{1}{2\pi}\sqrt{\frac{k}{m}}$& natural frequency of the system \\
$\omega_n= 2 \pi f$& natural frequency of the system  \\
$D$ & characteristic length of the body  \\
$m^*=\frac{m}{\rho \times \text{Volume of the body}}$& mass ratio \\
$U^*=\frac{U}{f \times D}$& reduced velocity  \\
$\zeta= \frac{c}{2 m \omega_n}$& damping ratio \\
$P_t$   & power transferred to the body by the fluid \\
$P_d$& power dissipated due to mechanical damping  \\
$Re$& Reynolds number  \\
$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle \\
& \\
& \\
\end{tabular}

### 2013-11-19 research/paper/results/results-2.3.tex
uploaded with Kenny's corrections

 The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ (Fig.\ref{fig:uncollapsed_data} (a) and (b)). The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers. This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}. Hysteresis could be observed for the case with a higher Reynolds number. This was achieved by manipulating the initial conditions (initial displacement) of the system. The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude. Although a third state could be achieved theoretically, it was not possible to achieve numerically. This was also observed by \cite{Vio2007}.

@@

 The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$. The value of  \ustar at which the peak power occur increases with $\zeta$. However, the magnitude of the peaks remain constant for all the values of $\zeta$.  \cite{Barrero-Gil2010a} also showed a similar trend. The higher Reynolds number case clearly showed hysteresis in the power data. The range of hysteresis tend to increase with increasing $\zeta$. It could be observed that unlike VIV the  system has no preferred frequency. Although the onset of galloping and the point where peak power occur at different $U^*$ when the damping ratio is changed, the peak power remains constant regardless of $U^*$. The efficiency of the system could defined as the ratio of $P_m$ and the energy of the fluid per unit length which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}). It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300. The peak efficiency in \cite{Barrero-Gil2010a} is approximatly $5\%$ than what this study obtained. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near the maximum force compared to the $7^{th}$ order polynomial used in this study

@@

 Now the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective. The shedding forces can be neglected because the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency, for the cases that exhibit galloping. It is obvious that the forcing term on LHS of the equation is only dependent on transverse velocity($\dot{y}$) which is essentially the input power of the system. On the RHS, the mechanical damping or system damping is the only term that takes out power at any instant. This could be expressed as the product of the damping force and the velocity ($P_d$). The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period). Therefore the system is governed by the transverse velocity rather than the natural frequency.

@@

 The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve). These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $\frac{c}{\rho\mathcal{A}U}$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3. Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)

At region 2 ($U^*=165$). $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^0$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is a best compromise between region 1 and 3. The damping is substantially high to obtain a high power output while not too high to hinder the induced angle of attack entering the region where the forcing is high.

@@

At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$. The overall mean power tend to increase  as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.0.235$.It is estimated that the efficiency limit i.e $\ustar \rightarrow \infty$  and $m^* \rightarrow 0$ will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing. Physical systems may not realize the full potential due to practical limitations. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.

@@

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is function of $(\dot{y})^2$ the error between QSS and FSI power becomes significantly large.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system. This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters). By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165. The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300. The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. The cause for this was found out to be the fact that when the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.

>>>>

 The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ (Fig.\ref{fig:uncollapsed_data} (a) and (b)). The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers. This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}. Hysteresis could be observed for the case with a higher Reynolds number. Different solutions could be obtained by manipulating the initial conditions (initial displacement) of the system. The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude. Although a third state could be simulate theoretically, it was not possible to achieve numerically. This was also observed by \cite{Vio2007}.

@@

 The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$. The value of  \ustar at which the peak power occur increases with $\zeta$. However, the magnitude of the peaks remain constant for all the values of $\zeta$.  \cite{Barrero-Gil2010a} also observed a similar behaviour. The higher Reynolds number case clearly showed hysteresis in the power data. The range of hysteresis tend to increase with increasing $\zeta$. It could be observed that unlike VIV the  system has no preferred frequency. Although the onset of galloping and the point where peak power occur at different $U^*$ values when the damping ratio is varied, the peak power remains constant regardless of $U^*$. The efficiency of the system could defined as the ratio of the time average power output to $P_{mean}$ the kinetic energy in the fluid per which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}). It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300. The peak efficiency in \cite{Barrero-Gil2010a} is approximately $5\%$ than what this study obtained. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.

@@

 Now the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective. The shedding forces can be neglected because the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency, for the cases that exhibit galloping. It is obvious that the forcing term on LHS of the equation is only dependent on transverse velocity($\dot{y}$) which is essentially the input power of the system. On the RHS, the mechanical damping or system damping is the only term that takes out power at any instant. This could be expressed as the product of the damping force and the velocity ($P_d$). The inertia and the stiffness terms governs the frequency of the system but the forces associated with those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period). Therefore the system is governed by the transverse velocity rather than the natural frequency.

@@

 The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve). These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $\frac{c}{\rho\mathcal{A}U}$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3. Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. The maximum amount of power that could be transferred occurs near the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)

At region 2 ($U^*=165$). $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^0$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is a best compromise between region 1 and 3. The damping is substantially high to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.

@@

At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$. The overall mean power tend to increase  as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing. Physical systems may not realize the full potential due to practical limitations. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.

@@

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is a function of $(\dot{y})^2$ the error between QSS and FSI power is compounded.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. At higher $m^*$ ($m^8>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ . By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165. The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300  when $\frac{c}{\rho \mathcal{A}U}=0.314$ and $\frac{c}{\rho \mathcal{A}U}=1.04$ respectively. The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output. The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$
